---
title: "Prediction intervals based on historical control data obtained from bioassays"
author: "Max Menssen"
date: "09/12/2021"
output: 
  beamer_presentation:
    keep_tex: true
    includes:
      in_header: preamble.tex      

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

## Contents

Introduction 

- Motivating example (Avian repro)
- Definitions 
- Fields of application 
- HCD in toxicology 


Methods 

- Available methods in 2017 
- Prediction intervals 
- Bootstrap calibration 


## Contents

Results

- Simulations
- Implementations

Discussion

- M>1

Further research

- Generalized linear random effects models
- Tolerance intervals



## 

\center{Introduction}

## Motivating example
Bla bla bla

## Definition of bioassays


```{r echo=FALSE, message=FALSE, fig.height=3, cache=TRUE}
h <- "h=1"
treat <- c("contr.", "dose 1", "dose 2", "dose 3")
fill <- c("#3366CC", "#FF9933", "#FF9933", "#FF9933")

dat <- data.frame(h=h,
                  treat=treat, 
                  fill=fill)

ggplot(dat, aes(x=treat, 
                y=factor(h)))+
  theme_bw()+
  geom_tile(fill=fill,
            size=3,
            color="black")+
  geom_text(aes(label=treat), size=10)+
  # facet_grid(h~.)+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
  


```


## Historical control data

```{r, message=FALSE, fig.height=3, cache=TRUE}
h <- c(rep("h=1", 4),
       rep("h=2", 4),
       rep("h=3", 4),
       rep("h=4", 4),
       rep("h=5", 4))
y="1"
treat <- rep(c("contr.", "dose 1", "dose 2", "dose 3"), 5)
fill <- c("#3366CC", "#FF9933", "#FF9933", "#FF9933",
          "#3366CC", "#CC6600", "#CC6600", "#CC6600",
          "#3366CC", "#CC9966", "#CC9966", "#CC9966",
          "#3366CC", "#CC9933", "#CC9933", "#CC9933",
          "#3366CC", "#FFCC66", "#FFCC66", "#FFCC66")

dat_hist <- data.frame(h=h,
                  treat=treat, 
                  fill=fill)

ggplot(dat_hist, aes(x=treat, 
                y=y))+
  theme_bw()+
  geom_tile(fill=fill,
            size=3,
            color="black")+
  geom_text(aes(label=treat), size=5)+
  facet_grid(h~.,
             switch="both")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        
        strip.text.y = element_text(size = 15, 
                                    face = "bold"),
        strip.text.y.left = element_text(angle = 0))
  

```




## 

\center{Methods}

## Overdispersed binomial data

Binomial
$$ var(y_i)= n_i \pi (1 - \pi) $$
Quasi-Binomial
$$ var(y_i)= \phi n_i \pi (1-\pi)$$

Beta-Binomial
$$ var(y_i)= n_i \pi (1 - \pi) [1+ (n_i-1)\rho]$$



